Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-14 paper/ms.tex
Expand on limitations of actions

The transformation to action space is not trivial, and many of the assumptions
of the transformation are potentially incorrect. It is therefore natural to
consider the reason to transform to action space. One reason is dimensionality
reduction --- in the action space paradigm, a stellar orbit is completely
described by three actions, as opposed to six dimensions of phase space. This
means that the relationship between {\em orbital} properties of individual
stars and stellar properties such as age or metallicity can be investigated.

We explore one science goal that relies on the conservation of actions --- the
reconstruction of open clusters across large distances using dynamical
tagging. The basic program is to match stars with roughly the same actions. To
set the scene, we consider the orbits of the nine open clusters within
$250\,\pc$ as reported by the {\em Gaia} collaboration
\citep{2018A&A...616A..10G}. In Table~\ref{tab:real_clusters}, we report the
distance to each cluster, the three actions, and the maximum vertical extent
of their orbits ($z_{\text{max}}$). The actions are computed using the
technique described in Section~\ref{ssec:action_comp}.

@@

To provide one such realization of a realistic Galactic potential, we turn to
cosmological zoom-ins of Milky Way-mass galaxies from the Feedback in
Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} (the Latte suite
of simulations).

>>>>

The transformation to action space is not trivial, and many of the assumptions
of the transformation are potentially incorrect. For instance, the assumption
that the Galactic potential is axisymmetric may be inadequate with current
measurement errors. Even if this assumption is valid, the parameters used in
our axisymmetric models may be inadequately tuned to observations. In
addition, the necessity of 6D phase space measurements of a star limits the
Galactic volume observable in action space.

With these limitations in mind, it is therefore natural to consider the reason
to transform to action space. One reason is dimensionality reduction --- in
the action space paradigm, a stellar orbit is completely described by three
actions, as opposed to six dimensions of phase space. This means that the
relationship between {\em orbital} properties of individual stars and stellar
properties such as age or metallicity can be investigated.

We explore one science goal that relies on the conservation of actions --- the
reconstruction of open clusters across large distances using dynamical
tagging. The basic program is to match stars with roughly the same actions as
their supposed natal cluster. To set the scene, we consider the orbits of the
nine open clusters within $250\,\pc$ as reported by the {\em Gaia}
collaboration \citep{2018A&A...616A..10G}. In Table~\ref{tab:real_clusters},
we report the distance to each cluster, the three actions, and the maximum
vertical extent of their orbits ($z_{\text{max}}$). The actions are computed
using the technique described in Section~\ref{ssec:action_comp}.

@@

To provide a realization of a realistic Galactic potential, we turn to
cosmological zoom-ins of Milky Way-mass galaxies from the Feedback in
Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} (the {\em Latte} suite
of simulations).
